MS Technical Paper: \\ Placement Algorithms for Heterogeneous FPGAs

### 2025-09-03 latex/paper/sections/12-future_work.tex
finish the abstract

As noted in Section~\ref{sec:placement}, replacing SA with AP requires splitting the placement stage into two substages:  
\emph{global placement}, which determines continuous target positions using analytical optimization, and  
\emph{detailed placement} (legalization), which snaps objects to valid \texttt{site}s while adhering to hardware constraints.  
Global placement can be performed using any number of off-the-shelf (OTS) analytical solvers.

>>>>

As noted in Section~\ref{sec:placement}, replacing SA with AP requires splitting the placement stage into two substages:  
\emph{global placement}, which determines continuous target positions using analytical optimization, and  
\emph{detailed placement} (legalization), which snaps objects to valid \texttt{site}s while adhering to hardware constraints.  
Global placement can be performed using any number of off-the-shelf (OTS) analytical solvers, but detailed placement requires custom implementation tailored to the hardware.
We repeatedly loop through global placement into detailed placement until HPWL minimization slows to a stop.
